Operational Feature Selection in Gaussian Mixture Models

### 2016-09-29 paper.tex
fin de la SII-A-1

        A measure of good classification is based on an error matrix $M$, or \emph{confusion matrix}~\cite[Chapter 4]{congalton2008assessing}. An element $M_{ij}$ of the matrix represents the number of samples of class $i$ classified as class $j$. The confusion matrix allows the computation of several global and per-class indices related to the classification accuracy~\cite{congalton2008assessing}. Three global criteria were used 
        \begin{itemize}
        \item  \emph{The overall  accuracy} (OA)  is the  rate of  the
          number of samples with the  correct predicted label over the
          total  number of  samples~\cite{congalton2008assessing}. This
          metric is  easy to interpret  but is  biased in the  case of
          unbalanced classes.

@@

        In order to estimate classification rate, a cross-validation process over training set is used\cite{opac-b1127878}. The training set is divided in k folds, then, the training is done with $(k-1)$ folds and the performances are estimated with the remaining fold.

@@

        \subsubsection{Similarity between distributions}

        \hspace{0pt} \\
        The second type of criterion functions is a measure of similarity between two distributions. These measures are called divergence function and are defined so that, if $S$ is a space of all probability distribution with same support, it satisfies
        \begin{align*}
            &\forall (p,q) \in S, \text{Div}(p,q) \geq 0, \\
            &\text{Div}(p,q) = 0 \Leftrightarrow p = q.
        \end{align*}
        More specifically, focus is made on two particular divergences: the Kullback–Leibler divergence and the Jeffries–Matusita distance. The advantage of these divergences is that they have an explicit expression in the case of Gaussian models. The simplification allows to get rid of any integration calculus which is a major problem when dealing with high-dimensional data.

>>>>

        A measure of correct classification is based on an error matrix $M$, or \emph{confusion matrix}~\cite[Chapter 4]{congalton2008assessing}. An element $M_{ij}$ of the matrix represents the number of samples of class $i$ classified as class $j$. The confusion matrix allows the computation of several global and per-class indices related to the classification accuracy~\cite{congalton2008assessing}. Three global criteria were used 
        \begin{itemize}
        \item  \emph{The overall  accuracy} (OA)  is the  rate of  the
          number of samples with the  correct predicted label over the
          total  number of  samples~\cite{congalton2008assessing}. This
          metric is  easy to interpret  but is  biased in the  case of
          unbalanced classes.

@@

      The classification rate is  estimated by a $k$- cross-validation
      ($k$-CV)~\cite{opac-b1127878}.  To compute  the $k$-CV, a subset
      is removed  from $\mathcal{S}$ and  the GMM is learned  with the
      remaining training samples.   A test error is  computed with the
      removed  training  samples  used  as  validation  samples.   The
      process is  iterated $k$ times and  the estimated classification
      rate is computed as the mean  test error over the $k$ subsets of
      $\mathcal{S}$.

@@

        \subsubsection{Similarity between distributions}
        These measures are called divergence function and are defined so that, if $S$ is a space of all probability distribution with same support, it satisfies
        \begin{align*}
            &\forall (p,q) \in S, \text{Div}(p,q) \geq 0, \\
            &\text{Div}(p,q) = 0 \Leftrightarrow p = q.
        \end{align*}
        More specifically, focus is made on two particular divergences: the Kullback–Leibler divergence and the Jeffries–Matusita distance. The advantage of these divergences is that they have an explicit expression in the case of Gaussian models. The simplification allows to get rid of any integration calculus which is a major problem when dealing with high-dimensional data.
